Microlensing as a possible probe of the internal structure of quasars

### 2015-07-09 paper1/ms.tex
Theory edits
two columns?
some edits
affiliation changes

\documentclass[usenatbib,onecolumn]{mn2e}

\usepackage{amsmath}
\usepackage{graphicx}

@@

\author[I. Mohammed et al.] {Irshad Mohammed\thanks{irshad@physik.uzh.ch}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,
\newauthor
Prasenjit Saha,$^1$ and Joachim Wambsgans$^2$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

>>>>

\documentclass[usenatbib]{mn2e}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multicol}

@@

\author[Tomozeiu et al]{Mihai Tomozeiu$^{1,2}$,Irshad Mohammed$^1$, Manuel Rabold$^{1,2}$,
\newauthor
Prasenjit Saha$^1$ and Joachim Wambsganss$^3$\\
$^1${Physik-Institut, University of Zurich, Winterthurerstrasse 190,
  8057 Zurich, Switzerland} \\
$^2${Institute for Computational Science, University of Zurich,
  Winterthurerstrasse 190, 8057 Zurich, Switzerland} \\
$^3${Zentrum f\"ur Astronomie der Universit\"at Heidelberg,
  M\"onchhofstrasse 12--14, 69120 Heidelberg, Germany}
}
